---
title: "STA426_Exercise_1b"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readxl)
library(ggplot2)
library(stats)
```

***

## Exercise 1b Log-Normal Distributions

Let's study log-normal distributions today! The log-normal distribution is a continuous probability distribution of a random variable whose logarithm is normally distributed and takes only positive real values.

First, let's sample 100 values from a log-normally distributed variable and study the mean and the variance of our sample.

```{r sample}

sample <-as.data.frame(rlnorm(100, meanlog = 1, sdlog = 0.25))

colnames(sample) <- "value"

mean(sample$value)
var(sample$value)


```

Nice, now we have our data frame with 100 samples from a log-normal distributed variable with a mean of `r mean(sample$value)` and a variance of `r var(sample$value)`.

Now let's plot our sample as a histogram to visualise it.


```{r histogram}

ggplot(data=sample, aes(value)) + 
  geom_histogram(bins = 20)+
  theme_bw()

```


The hitogram is not really symmetric, it's kind of leaning to the left. 
How does it look like, if we plot it on a logarithmic x axis?


```{r log histogram}

ggplot(data=sample, aes(value)) + 
  geom_histogram(bins = 20)+
  scale_x_log10()+
  theme_bw()

```

Ah, that looks very much like a normal distribution, how nice.


